### 2018-03-24 README.Rmd
Add standardized slope (t)

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first:

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
use the package.

@@

***

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/andrewpbray/infer/blob/master/CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.Date()`.

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
use the package. By participating in this project you agree to abide by its terms.

@@
